---
title: "Main"
author: "Yuehan Kong (yk2756)"
date: "4/9/2018"
output: pdf_document
---

# Memory-Based Algorithms

### Step 0: Install necessary packages
```{r, message=FALSE}
list.of.packages <- c("MCMCpack", "ggplot2", "readr")

packages.needed=setdiff(list.of.packages, 
                        intersect(installed.packages()[,1], 
                                  list.of.packages))
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

library("MCMCpack")
library("ggplot2")
library("readr")
```

### Step 1: Load Processed Data
```{r}
setwd("~/Desktop/GR 5243/Project/Project4/doc")

train_1 <- read.csv("../data/data_matrix/train_1.csv", header = T)
train_2 <- read.csv("../data/data_matrix/train_2.csv", header = T)
test_1 <- read.csv("../data/data_matrix/test_1.csv", header = T)
test_2 <- read.csv("../data/data_matrix/test_2.csv", header = T)

source("../lib/memory_based.R")
source("../lib/evaluation.R")

train_1 <- data_process(train_1)
train_2 <- data_process(train_2)
test_1 <- data_process(test_1)
test_2 <- data_process(test_2)
```

### Step 2: Similarity Weight
##### Pearson correlation & Spearman correlation
```{r, message=FALSE, warning=FALSE}
#w_pearson_1 <- sim_weight(train_1,"pearson") 
#w_pearson_2 <- sim_weight(train_2,"pearson")
#w_spearman_1 <- sim_weight(train_1, "spearman")
#w_spearman_2 <- sim_weight(train_2, "spearman")

#w_pearson_1[is.na(w_pearson_1)] = 0
#w_pearson_2[is.na(w_pearson_2)] = 0
#w_spearman_1[is.na(w_spearman_1)] = 0
#w_spearman_2[is.na(w_spearman_2)] = 0

#saveRDS(w_pearson_1, file = "../output/w_pearson_1.RData")
#saveRDS(w_pearson_2[1:2528,], file = "../output/w_pearson_2(1).RData")
#saveRDS(w_pearson_2[2529:5055,], file = "../output/w_pearson_2(2).RData")
#saveRDS(w_spearman_1, file = "../output/w_spearman_1.RData")
#saveRDS(w_spearman_2[1:2528,], file = "../output/w_spearman_2(1).RData")
#saveRDS(w_spearman_2[2529:5055,], file = "../output/w_spearman_2(2).RData")

w_pearson_1 <- read_rds("../output/w_pearson_1.RData")
w_pearson_2_1 <- read_rds("../output/w_pearson_2(1).RData")
w_pearson_2_2 <- read_rds("../output/w_pearson_2(2).RData")
w_pearson_2 <- rbind(w_pearson_2_1, w_pearson_2_2)

w_spearman_1 <- read_rds("../output/w_spearman_1.RData")
w_spearman_2_1 <- read_rds("../output/w_spearman_2(1).RData")
w_spearman_2_2 <- read_rds("../output/w_spearman_2(2).RData")
w_spearman_2 <- rbind(w_spearman_2_1, w_spearman_2_2)
```

##### SimRank
```{r}
#w_simrank_2 <- read.csv("../output/usersim_final.csv")
load("../output/user_sim1.RData")
load("../output/user_sim2.RData")
w_simrank_2 <- rbind(user1,user2)
user_lst <- w_simrank_2[,1]
w_simrank_2 <- w_simrank_2[,-1]
colnames(w_simrank_2) <- user_lst
rownames(w_simrank_2) <- user_lst
```

### Step 3: Variance Weighting
```{r}
var_1 <- read_rds("../output/variance_weight_1.RData") # MS Dataset
var_2 <- read_rds("../output/variance_weight_2.RData") # Movie Dataset
```

### Step 4: Selecting Neighborhoods & Rating Normalization
##### Selecting Neighborhoods: Weight thresholding
##### Rating Normalization: Deviation from mean

```{r}
### Pearson
neighbor_pearson_1 <- select_neighbors(w_pearson_1)
neighbor_pearson_2 <- select_neighbors(w_pearson_2)
pred_pearson_1 <- prediction_1(weight = w_pearson_1, list_neighbors = neighbor_pearson_1)
pred_pearson_2 <- prediction_2(weight = w_pearson_2, list_neighbors = neighbor_pearson_2)

### Spearman
neighbor_spearman_1 <- select_neighbors(w_spearman_1)
neighbor_spearman_2 <- select_neighbors(w_spearman_2)
pred_spearman_1 <- prediction_1(weight = w_spearman_1, list_neighbors = neighbor_spearman_1)
pred_spearman_2 <- prediction_2(weight = w_spearman_2, list_neighbors = neighbor_spearman_2)

### SimRank
w_simrank_2 <- as.matrix(w_simrank_2)
neighbor_simrank_2 <- select_neighbors(weight = w_simrank_2, thresholding = 0.006)
pred_simrank_2 <- prediction_2(weight = w_simrank_2,list_neighbors = neighbor_simrank_2)

### Pearson + Variance
w_var_pearson_1 <- w_pearson_1*var_1 
w_var_pearson_2 <- w_pearson_2*var_2
neighbor_w_var_pearson_1 <- select_neighbors(w_var_pearson_1)
neighbor_w_var_pearson_2 <- select_neighbors(w_var_pearson_2)
pred_w_var_pearson_1 <- prediction_1(weight = w_var_pearson_1, list_neighbors = neighbor_w_var_pearson_1)
pred_w_var_pearson_2 <- prediction_2(weight = w_var_pearson_2, list_neighbors = neighbor_w_var_pearson_2)

### Spearson + Variance
w_var_spearman_1 <- w_spearman_1*var_1
w_var_spearman_2 <- w_spearman_2*var_2
neighbor_w_var_spearman_1 <- select_neighbors(w_var_spearman_1)
neighbor_w_var_spearman_2 <- select_neighbors(w_var_spearman_2)
pred_w_var_spearman_1 <- prediction_1(weight = w_var_spearman_1, list_neighbors = neighbor_w_var_spearman_1)
pred_w_var_spearman_2 <- prediction_2(weight = w_var_spearman_2, list_neighbors = neighbor_w_var_spearman_2)

### SimRank + Variance
w_var_simrank_2 <- w_simrank_2*var_2
w_var_simrank_2 <- as.matrix(w_var_simrank_2)
neighbor_var_simrank_2 <- select_neighbors(weight = w_var_simrank_2, thresholding = 0.006)
pred_w_var_simrank_2 <- prediction_2(weight = w_var_simrank_2,list_neighbors = neighbor_var_simrank_2)
```

### Step 5: Evaluation
##### MAE 
```{r}
### Movie Dataset
mae_pearson_2 <- mae(pred_pearson_2, test_2)
mae_spearman_2 <- mae(pred_spearman_2, test_2)
mae_simrank_2 <- mae(pred_simrank_2,test_2)
mae_w_var_pearson_2 <- mae(pred_w_var_pearson_2, test_2)
mae_w_var_spearman_2 <- mae(pred_w_var_spearman_2, test_2)
mae_w_var_simrank_2 <- mae(pred_w_var_simrank_2, test_2)

mae_pearson_2
mae_spearman_2
mae_simrank_2
mae_w_var_pearson_2
mae_w_var_spearman_2
mae_w_var_simrank_2
```

##### Rank Score
```{r}
### MS Dataset
rankscore_pearson_1 <- rank_score(pred_pearson_1, test_1)
rankscore_spearman_1 <- rank_score(pred_spearman_1, test_1)
rankscore_w_var_pearson_1 <- rank_score(pred_w_var_pearson_1, test_1)
rankscore_w_var_spearman_1 <- rank_score(pred_w_var_spearman_1, test_1)

rankscore_pearson_1
rankscore_spearman_1
rankscore_w_var_pearson_1
rankscore_w_var_spearman_1
```

### Step 6: Plotting Main Results
```{r}
### MS Dataset
method_1 <- c("pearson", "spearman", "pearson", "spearman")
wet_1 <- c("none", "none", "var", "var")
r_1 <- c(35.74765, 35.73527, 42.65232, 42.652)
ms <- data.frame(Method = method_1, Weights = wet_1, RankScore = r_1)

ggplot(data = ms, aes(x=Weights, y=RankScore, group = Method, colour = Method)) +
  geom_point() +
  geom_line() +
  labs(title = "Rank Score for MS")

### Movie Dataset
method_2 <- c("pearson", "spearman", "simrank", "pearson", "spearman", "simrank")
wet_2 <- c("none", "none", "none", "var", "var", "var")
mae_2 <- c(1.083907, 1.074416, 1.043124, 1.068813, 1.069592, 1.141436)
movie <- data.frame(Method = method_2, Weights = wet_2, MAE = mae_2)

ggplot(data = movie, aes(x=Weights, y=MAE, group = Method, colour = Method)) +
  geom_point() +
  geom_line() +
  labs(title = "MAE for Movie")
```


# Model-Based Algorithm

### Step 1: Load Processed Data
```{r}
train_ms <- read.csv("../data/data_matrix/train_1.csv", header = T)
test_ms <- read.csv("../data/data_matrix/test_1.csv", header = T)
source("../lib/model_based.R")
```

### Step 2: Prediction
```{r}
pred_cluster<-cluster(train_ms,test_ms)
```


### Step 3: Evaluation: Rank Score
```{r}
rank_score(pred_cluster,as.matrix(test_ms[,3:ncol(test_ms)]))
```










